Empirical Option Returns and the risk-free Rate in Crypto Asset Markets

### 2024-01-23 written/paper.tex
writing methodology section. some prints for ana.

We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. We use it as a benchmark that beta-neutral portfolios should yield. 
We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for particular levels of moneyness. We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., high premia.of at-the-money options. The effect holds after compensating for market crash insurance and transaction cost. 
We assess the deadweight loss due to observed risk premia and propose a simple trading strategy that exploits this particular inefficiency.

@@

In accordance with Shumway, we follow the argument that any beta-neutral portfolio should yield the risk-free rate. We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so, that the sum of option betas yields zero. 
The underlying data are executed transactions. All option greeks remain constant except time-to-maturity. Any transaction has a time-to-maturity (tau) "reset"/synced to settlement time. All options are bought and held until settlement at 10am UTC. To match always a call and a put with an equal strike price for a straddle, we use Put-Call-Parity to ensure the existence of each straddle.  
The empirical performance of the resulting zero-beta straddles is assessed on a daily base.

@@

@@

@@

>>>>

We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. We use it as a benchmark that beta-neutral portfolios should yield. 
We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for at-the-money instruments. We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., high premia.of at-the-money options. The effect holds after compensating for market crash insurance and transaction cost. 
We assess the deadweight loss due to observed risk premia and propose a simple trading strategy that exploits this particular inefficiency.

@@

We follow the argument that any beta-neutral portfolio should yield the risk-free rate. We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero. The straddle's payoff $r_v$ is depicted in Equation 1, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$. The weight $\theta$ is found by solving Equation 2 through Equation 3. The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\delta$, the Black-Scholes option price $C$ and the market beta $\beta_m (=1)$ as depicted in Equation 4. 
The underlying data are executed transactions. All option greeks remain constant except time-to-maturity. Any transaction has a time-to-maturity (tau) "reset"/synced to settlement time. All options are bought and held until settlement at 10am UTC. 
We match our universe of straddles as follows:
Per definition, a straddle exists of a call and a put with similar strike and maturity. We construct the set of empirical straddles by iterating over our list of executed calls and puts. For each call (put), we use Put-Call-Parity to complete the straddle. 
The empirical performance of the resulting zero-beta straddles is assessed on a daily base. We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed. For each level of moneyness m, we construct an interval $[m, m + 0.05]$. We condition daily returns on over levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero. We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.

- Formulas for the weights!

Straddle Return $r_v$￼, Share of Straddle’s value in Call Options ￼$\theta$,
Call and Put market Beta ￼$\beta_c$, $\beta_p$.

\begin{equation}
r_v = \theta r_c + (1-\theta)r_p
\end{equation}

\begin{equation}
\theta \beta_c + (1-\theta)\beta_p = 0\\
\end{equation}

\begin{equation}
\theta = \frac{-\beta_p}{\beta_c - \beta_p}\\
\end{equation}

\begin{equation}
\beta_c = \frac{s}{C} \Delta \beta_s\\
\end{equation}

We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events. Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles. 
Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
Close Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility (which is more than empirically justified.)
Maybe make a summary of the relationship between ATM and 20\% OTM premium.

The performance of the vanilla and crash-resistant straddles is evaluated with and without fees. Clearly, application of the fees constitutes simply a linear shift, which is well-visible in the graphs. 
The return of the straddles until settlement is re-scaled on a daily level. It is plotted as a boxplot of daily returns for each level of moneyness in the interval [0.7, 1.3]. 
Fees are standard option fees on Deribit. We assume using an option combo fee, which makes the a spread's cheaper leg free of charge. 
Consequently, the trading fee for one option spread would be the lesser of 0.0003 Bitcoin or 12.5\% of the more expensive option price. All fees are converted into USD based on the BTC/USDT exchange rate around settlement time.

@@

We impose a maximum IV of 2.5

@@

The actual annualized returns of such a carry trade would be

Table:

Year, Currency, Exchange, Annual Return

@@

Compare to weekly 0.5\% loss observed in equity options.
